Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-23 journal/article.tex
S: Previous culture like agile

>>>>

% Previous culture is like agile

A few organizations had already some structures in place that were similar to
agile, which made the transformation easier.
For instance, a previous organizational model based on small and autonomous
teams strongly aided the adoption [P3].
Another case described the original on-demand delivery model a natural fit for
agile, and the transformation was presented as a return to core values instead
of a remodeling [P16].
% The agile culture must also be maintained in each step of the transformation
% [P31]
